Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-04-04 cikm2016/intro.tex
CIKM formatting

Our solution was to develop two machine learning algorithms for automatically deriving the format string from the user's data with over 95\% parsing accuracy. We developed two algorithms because we were not aware of any previous work on this problem and we needed to be able to cross-validate our results on a large testing corpus. Either approach allows the user to simply specify ``this column is a date" and the visualization system can respond quickly and accurately enough to avoid interrupting the user's cognitive flow.

>>>>

Our solution was to develop two algorithms for automatically deriving the format string from the user's data with over 95\% parsing accuracy. Both algorithms are built based on classical machine learning algorithms that learn from pattern recognition to make data-driven predictions. We developed two algorithms because we were not aware of any previous work on this problem and we needed to be able to cross-validate our results on a large testing corpus. Either approach allows the user to simply specify ``this column is a date" and the visualization system can respond quickly and accurately enough to avoid interrupting the user's cognitive flow.

### 2016-04-04 cikm2016/relatedwork.tex
CIKM formatting

%\subsection{Previous Work}

@@

\subsection{Contributions}

Our work differs from these previous methods for parsing date-time expressions as we are using an entire column of data as context without the necessary presence of rich lexical identifiers to determine temporal context. This sort of data tends to be prevalent in datasets that are used in visualizations.

In particular, our contributions are:
\begin{itemize}
\item By analysing an on line corpus, we provide evidence that practical date parsing requires the ability to recognise hundreds of formats;
\item We show how to extend prior work on Minimum Descriptive Length structure extraction to generate a freely available date format domain language with over 90\% accuracy;
\item We describe a second Natural Language Processing technique for generating the same date format domain language with similar accuracy. We describe how the basic algorithm is extended to support grammar variants and constraints unique to date formats. The parsing algorithm is extended to compute an overall dominant pattern over a data column;
\item We describe some limitations of this domain language that would improve its utility.
\end{itemize}

>>>>

@@

Our work differs from these previous methods for parsing date-time expressions as we are using an entire column of data as context without the necessary presence of rich lexical identifiers to determine temporal context. This kind of data tends to be prevalent in datasets that are used in visualizations.
